Motorcycle Acceleration example

### 2019-12-18 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

Apply SMASH again, this time assuming equal variances
-----------------------------------------------------

Apply SMASH (assuming equal variances) to the Motorcycle Accident data
set.

@@

@@

Apply TI thresholding to the Motorcycle Accident data set.

@@

@@

Compare results from all methods
--------------------------------

And in this next plot, we compare the SMASH estimates (the orange
line) against the the mean estimates obtained by TI thresholding (dark
blue line), and TI thresholding when the variances have been estimated
by SMASH (dotted green line).

```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
      col = "darkblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

The TI thresholding estimate and the SMASH estimate with homoskedastic
variances both show notable artifacts. When the TI thresholding method
is provided with the SMASH variance estimate, the mean signal is
substantially smoother.

>>>>

SMASH, homoskedastic vs. heteroskedastic
----------------------------------------

Apply SMASH, this time assuming equal variances, to the Motorcycle
Accident data set:

@@

While the estimates are similar, heteroskedastic SMASH yields a
noticeably smoother curve.

@@

Apply TI thresholding to the Motorcycle Accident data set. In this
first run, the variance is assumed to be constant.

@@

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated using the "median absolute deviation", or
RMAD, method.

```{r run-tithresh-rmad}
res.ti.rmad.mc <- tithresh.rmad.wrapper(x.ini.mc,y.ini.mc)
```

@@

Compare SMASH vs. TI thresholding
---------------------------------

In this next plot, we compare the SMASH estimates with heteroskedastic
variances (the same orange line as above) against the the mean estimates
obtained by TI thresholding with constant variance (solid dark blue
line), TI thresholding with RMAD variance estimates (solid light blue
line), and TI thresholding when the variances have been estimated by
SMASH (dotted green line).

```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
	 col = "darkblue")
lines(res.ti.rmad.mc$x,res.ti.rmad.mc$mu.est,lwd = 2,lty = "solid",
      col = "dodgerblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

The TI thresholding estimate, like the SMASH estimate with
homoskedastic variances, shows notable artifacts. When TI thresholding
estimates the variance using RMAD, or when it is provided with the
SMASH variance estimate, the mean signal is substantially smoother.
